problem years

### 2024-08-19 src/problem_years_10.Rmd
lisa10

ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  # scale_fill_discrete_c4a_cat(name = "%", palette = "parks.charmonix",
  #                             na.translate = FALSE) +
  scale_fill_manual(values = palette_new, na.value="white", breaks = NULL, drop = F) +
  theme_minimal() +
  theme(panel.grid.major = element_line(colour = "transparent"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank()) +
  #guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = "LISA, websites per firm in a LA") + 
  theme(legend.title=element_blank())

theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank())

@@

  ggplot(data = oa.uk, aes(fill = quadr$median)) +
    geom_sf(data = uk, fill = "white", linewidth = .5) +
    geom_sf(linewidth = 0) +
    geom_sf(data = tif_sf, fill = "black", size = .3) +
    #geom_sf_text(data = tif_sf, aes(label = name, fill = "black"), size = 4) +
    scale_fill_manual(values = palette_new, na.value="white", drop = F) +
    theme_minimal() +
    theme(panel.grid.major = element_line(colour = "transparent"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.title=element_blank()) +
          #legend.position="none") +
    guides(fill = guide_legend(reverse = TRUE)) +
    labs(title = t,
        subtitle = "LISA, websites per OA")

>>>>

ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  scale_fill_manual(values = palette_new, na.value="white", breaks = NULL, drop = F) +
  theme_minimal() +
  theme(panel.grid.major = element_line(colour = "transparent"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank()) +
  #guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = "LAD, ", t) + 
  theme(legend.title=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        plot.title = element_text(hjust = 0.5)) +
  theme(plot.title = element_text(size=20, face = "bold"))

@@

  ggplot(data = oa.uk, aes(fill = quadr$median)) +
    geom_sf(data = uk, fill = "white", linewidth = .5) +
    geom_sf(linewidth = 0) +
    geom_sf(data = tif_sf, fill = "black", size = .3) +
    #geom_sf_text(data = tif_sf, aes(label = name, fill = "black"), size = 4) +
    scale_fill_manual(values = palette_new, na.value="white", drop = F) +
    theme_minimal() +
    theme(panel.grid.major = element_line(colour = "transparent"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.title=element_blank()) +
          #legend.position="none") +
    #guides(fill = guide_legend(reverse = TRUE)) +
    labs(title = paste0("OA, ", t)) + 
    theme(legend.title=element_blank(),
          plot.margin = unit(c(0, 0, 0, 0), "cm"),
          plot.title = element_text(hjust = 0.5)) +
    theme(plot.title = element_text(size=20, face = "bold"))
